Generating Simulated Data

### 2021-03-12 docs/SimData.Rmd
generate diet data for MSSPM

```{r, write-msspm-diet}

@@

# aggregate over ages (survey diet is in proportion by age)

@@

trueB_age_allbox <- NOBAom_ms$truebio_ss %>%
  #sum over polygons
  #aggregate(dat$atoutput,list(dat$species,dat$agecl,dat$time, dat$prey),sum)
  group_by(species,agecl,time) %>%
  summarise(sum(atoutput))

>>>>

Diet composition is by predator age class for each time (unit=time.days) and is a proportion (sums to 1 for each time). We get species diet composition by aggregating over age classes (weight diet composition at age by true biomass at age).

```{r, write-msspm-diet, eval=FALSE}

@@

# divide time.days by runpar$toutinc to match time in biomass
# aggregate over ages using true biomass at age (survey diet is in proportion by age)

@@

trueB_age_allbox <- NOBAom_ms$truebio_ss %>%
  #sum over polygons
  #aggregate(dat$atoutput,list(dat$species,dat$agecl,dat$time, dat$prey),sum)
  group_by(species,agecl,time) %>%
  summarise(trueBatage = sum(atoutput))

trueB <- trueB_age_allbox %>%
  group_by(species, time) %>%
  summarise(trueB = sum(trueBatage))

trueBagecl <- merge(trueB_age_allbox, trueB)

#multiple surveys named in list object, use as filename
for(s in names(all_diets)){
  #arrange into wide format: year, Species1, Species2 ... and write csv
  svdiet <- all_diets[[s]][[1]] %>%
    #calc_timestep2time(d.name, ., run.prm.file) %>% #this gives an arbitrary start year of 1970
    dplyr::mutate(time = time.days/NOBAom_ms$runpar$toutinc) %>%
    dplyr::left_join(., trueBagecl) %>%
    dplyr::mutate(dietBwt = dietSamp*trueBatage) %>%
    dplyr::group_by(species,time,prey,trueB) %>%
    dplyr::summarise(totdietBwt = sum(dietBwt)) %>%
    dplyr::mutate(totdietComp = totdietBwt/trueB) %>%
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::ungroup() %>%
    dplyr::select(year, species, prey, totdietComp) %>%
    write_csv(paste0(o.name,"diet_",s,".csv"))
}
